\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09


\title{Implementing Dimensionality Reduction in Apache Flink using the Lanczos Algorithm}

\author{
Nik Hille \\
\texttt{nik.hille@campus.tu-berlin.de} \\
\And
Fridtjof Sander \\
\texttt{fridtjof.sander@campus.tu-berlin.de}
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\nipsfinalcopy % Uncomment for camera-ready version

\begin{document}

\begin{center}
\textbf{Advanced Information Management III Scalable Data - Analytics and Data Mining}
\end{center}

\vspace{0.8cm}

\maketitle

\vspace{0.8cm}


\begin{abstract}

We made some total crap.
\end{abstract}

\vfill

\begin{center}
\today
\end{center}

\pagebreak

\section{Introduction}

sdkjnasdknsjdknas  jknsdkjnasd kjasdkjnasdkjnasd jknasd

\section{Problem Statement}

\section{The Lanczos Algorithm}

\section{Approaches}

\section{Implementations}

\section{Results}

\section{Conclusion}


\subsubsection*{References}
\small{
[1] Alexander, J.A. \& Mozer, M.C. (1995) Template-based algorithms
for connectionist rule extraction. In G. Tesauro, D. S. Touretzky
and T.K. Leen (eds.), {\it Advances in Neural Information Processing
Systems 7}, pp. 609-616. Cambridge, MA: MIT Press.

[2] Bower, J.M. \& Beeman, D. (1995) {\it The Book of GENESIS: Exploring
Realistic Neural Models with the GEneral NEural SImulation System.}
New York: TELOS/Springer-Verlag.

[3] Hasselmo, M.E., Schnell, E. \& Barkai, E. (1995) Dynamics of learning
and recall at excitatory recurrent synapses and cholinergic modulation
in rat hippocampal region CA3. {\it Journal of Neuroscience}
{\bf 15}(7):5249-5262.
}

\end{document}
